Consistency scores in text data

### 2020-08-21 outputs/documents/paper.Rmd
glove code examples

Here, we follow @falbel2017word to implement a skip-gram model of Word2Vec through Keras. There are three steps in the Keras deep learning framework: 1) prepare the data; 2) define the model; and 3) train and evaluate the model. **(Ke-Li: Can we change this to be a different dataset please?)** Following these steps, we first downloaded the Google News dataset [@citegooglenews] and preprocess the text into tokens.

@@

Here we follow **CITE** to implement GloVe using the `keras` R package [@kerasglove]. The blog post is aimed to create a word embedding model for text classification. However, we will only use the guide create a embedding index and skip the steps of text classification. Instead of building a model for word embedding from scratch as we did for the skip-gram model of Word2Vec, here we are merely loading the Glove model and its pre-trained word vectors as an index. The word embedding index is then saved to an R environment.

**[As before, we need code and examples here]**

>>>>

Here, we follow @falbel2017word to implement a skip-gram model of Word2Vec through Keras. There are three steps in the Keras deep learning framework: 1) prepare the data; 2) define the model; and 3) train and evaluate the model. **(Ke-Li: Can we change this to be a different dataset please? Yes, I changed it to Google News for now, let's change it to an official data set that we will decide on later!)** Following these steps, we first downloaded the Google News dataset [@citegooglenews] and preprocess the text into tokens.

@@

Here we follow the blog post published by Keras [@kerasglove] to implement GloVe using the `keras` R package [@kerasglove]. The blog post is aimed to create a word embedding model for text classification. However, we will only use the guide create a embedding index and skip the steps of text classification. Instead of building a model for word embedding from scratch as we did for the skip-gram model of Word2Vec, here we are merely loading the Glove model and its pre-trained word vectors as an index. The word embedding index is then saved to an R environment.

To use GloVe in R, we first download the pre-trained GloVe vectors. The file comes in zip format, which needs to be unzipped:

```{r, eval=FALSE}
download.file('http://nlp.stanford.edu/data/glove.6B.zip',destfile = 'glove.6B.zip')
unzip('glove.6B.zip')
```

The next step is to load the GloVe vectors into R:

```{r, eval=FALSE}
vectors = data.table::fread('glove.6B.300d.txt', data.table = F,  encoding = 'UTF-8')
colnames(vectors) = c('word',paste('dim',1:300,sep = '_'))
```

The GloVe vectors are now available in R. We restructure the word vectors into a tibble data frame for easy access. The tibble dataset has 400,000 words and 301 dimensions to represent each word:

```{r, eval=FALSE}
as_tibble(vectors)
# A tibble: 400,000 x 301
```
